\documentclass[sectionsleft,centered,10pt]{res}

\usepackage{newcent} 
\usepackage{wasysym}

\usepackage[hidelinks,urlcolor=black,colorlinks=true]{hyperref}
\let\oldhref\href
\renewcommand{\href}[2]{\oldhref{#1}{\textbf{#2}}}

%\setlength{\textwidth}{8in} % Text width of the document
\RequirePackage[a4paper, margin=0.7in]{geometry}
\setlength{\resumewidth}{7in}
\newsectionwidth{1.2in}
%\hoffset=1in
%\resumewidth=6in
\let\sep\ataribox

\begin{document}
 
\moveleft\hoffset\vbox{\centering\makebox[\resumewidth][c]{
			\parbox{\resumewidth}{
				\centering
				\huge\textbf Tiarnach \'O Riada
				\normalsize \\
				\bigskip
				{\hrule width\resumewidth height 1pt}
				\medskip
					tiarnach.oriada@ucdconnect.ie
					\hfill\sep\hfill \href{https://github.com/TOR-}{github.com/TOR-}
					\hfill\sep\hfill (+353)\,89\,257\,0056
				\medskip
				{\hrule width\resumewidth height 1pt}
				}
		}}


%----------------------------------------------------------------------------------------

\begin{resume}

\section{EDUCATION}

{\sl \textbf{University College Dublin}}\hfill 2016-2021\\
{\sl BEng Electronic Engineering}\\
Final GPA 3.74/4.2, First Class Honours\\\\
{\sl \textbf{École polytechnique fédérale de Lausanne}}\hfill 2018-2019\\
{\sl Erasmus Exchange in Electronic Engineering}\\
%Designed systems with VHDL and C++. Studied digital system design.\\

\section{EXPERIENCE}
{\sl\textbf{EOFIS} \hspace{0.5cm}\oldhref{https://eofis.ie}{eofis.ie}\hfill May 2021-Present}\\
\emph{CTO, Co-Founder}
\begin{itemize}
	\item Responsible for technical aspects of company's success.
	\item Development of VueJS frontend and Python and AWS backend.
	\item As thesis implemented prototype cloud-based automated flashcard generation system from online sources.
\end{itemize}
{\sl\textbf{Irish Photonic Integration Centre , Tyndall National Inst.} \hfill June-August 2020}\\
\emph{Summer Bursary Student}
\begin{itemize}
	\item Designed and implemented photon time of flight simulation software.
	\item Collaborated with rest of biophotonics research team.
\end{itemize}
{\sl\textbf{Spanish Point Technologies} \hfill June-August 2017,2018; March-August 2019}\\
\emph{Developer, QA Intern}
\begin{itemize}
	\item Developing applications with C\#, JavaScript, NodeJs, Python and SQL.
	\item Developing post-deployment tests for React and REST web application.
	\item Coordinated testing of several long-running projects.
\end{itemize}

\section{PROJECTS}
\href{http://bit.ly/SPICEBAGsim}{bit.ly/SPICEBAGsim} a spice-like circuit simulator and gui in Python and FORTRAN.\\
\href{http://bit.ly/Fyftem}{bit.ly/Fyftem} a Forth interpreter, written in x86\_64 assembler.\\
\href{http://bit.ly/ChucklesOS}{bit.ly/ChucklesOS} the Chuckles Operating System. x86 single tasking operating system written in C and developed using GNU tools on Linux.\\
\href{http://bit.ly/LLProtocol}{bit.ly/LLProtocol} a link layer protocol performing reliable transmission over a faulty physical link; detects errors and ensures eventual receipt of data. Designed with a REST-like api and developed in a team of four as a class project in UCD.\\
\href{http://bit.ly/DomotiqueSimulation}{bit.ly/DomotiqueSimulation} a C++ simulation of a home automation system.\\

\section{SKILLS}
Captain of the UCD Judo club for the 2019-2020 year. Current PRO.\\
Experience with small to medium projects in Python, C, C++, Intel x86\_64 assembly, VHDL, and MATLAB.\\
% Below line is filler
Also Forth, C\#, R, MS SQL, Javascript, CSS and HTML.\\
Git source control software, GNU development tools.\\
Experience maintaining and developing personal and server Linux systems.\\
Speak French to the CEFR level B2 (Upper Intermediate) and have a working proficiency in Italian.
\section{INTERESTS}
Forth and Factor; applications of deep learning; Judo, BJJ; flute, tin whistle and guitar.

\if{0}
\section{REFERENCES}
\makebox[\textwidth]{
	\small
	\parbox[t]{0.3\textwidth}{
		John Corley\\
		(+353)\,1\,652\,2000\\
		%+353 86 837 8244\\
		\emph{CTO,\\Spanish Point Enterprises}\\
		East Pt Business Park, \\Clontarf, Dublin, Ireland
	}\hfill
	\parbox[t]{0.4\textwidth}{
		Sanathana Konugolu\\
		%(+353)\,86\,600\,3036\\
		sanathana.konugolu@tyndall.ie\\
		\emph{Postdoctoral Researcher,\\
			Tyndall\\CEO, BioPixS}\\
		Cork, Ireland
	}\hfill
	\parbox[t]{0.3\textwidth}{
	Brian Mulkeen\\
	%(+353)\,1\,716\,1926\\
	brian.mulkeen@ucd.ie\\
	\emph{Lecturer/Assistant Professor}\\
	School of Electrical \\
	\& Electronic Engineering\\
	UCD, Belfield, Dublin 4
	}
}
\fi
\end{resume}
\end{document}
